---
title: "Gaze Occurrence Comparison Gallery"
output: html_document
---

## What this produces

Reads the 4 MP4s produced by `x_group_heatmap_gifs.Rmd` (`data/leap_voe_data/gaze_heatmap_videos/gaze_occurrence/[trial_type]_occurrence_compare.mp4`), base64-encodes each one, and writes a single portable HTML file with them embedded inline as `<video>` data URIs (no external file dependencies -- the page can be opened, emailed, or moved anywhere on its own). Duck and shoe clips are laid out as expected/surprise pairs, side by side. Videos do NOT autoplay -- each starts on click via the native `<video>` controls.

## Output

`data/leap_voe_data/gaze_heatmap_videos/gaze_occurrence_comparison.html` (\~23MB, since base64 adds \~33% over the \~17MB of source MP4s combined).

```{r setup}
library(here)
library(base64enc)
```

```{r paths}
video_dir <- here("data", "leap_voe_data", "gaze_heatmap_videos", "gaze_occurrence")
out_path  <- here("data", "leap_voe_data", "gaze_heatmap_videos", "leap_voe_fix_heatmaps.html")

# Duck and shoe each get one row of expected | surprise, side by side.
pairs <- list(
  "Object Type 1 (Duck)" = c(Expected = "expected_duck", Surprise = "surprise_duck"),
  "Object Type 2 (Shoe)" = c(Expected = "expected_shoe", Surprise = "surprise_shoe")
)
```

`generation_info.csv` (written by `x_group_heatmap_gifs.Rmd`'s own last chunk) records when the videos were last rendered and how many distinct infants contributed a fixation to any of the 4 trial types -- read here for the page header. Falls back gracefully if that file is missing (e.g. this gallery script run against older videos, before that chunk existed).

```{r generation-metadata}
meta_path <- file.path(video_dir, "generation_info.csv")

if (file.exists(meta_path)) {
  meta <- read.csv(meta_path, stringsAsFactors = FALSE)
  generated_date <- format(as.POSIXct(meta$generated_at[1], format = "%Y-%m-%dT%H:%M:%SZ", tz = "UTC"), "%B %d, %Y")
  n_infants_included <- meta$n_infants_included[1]
} else {
  generated_date <- "unknown"
  n_infants_included <- "unknown"
}
```

`video_tag()` embeds one clip; `group_section()` wraps a pair (expected + surprise) into one labeled row.

```{r html-builders}
video_tag <- function(slug, label) {
  mp4_path <- file.path(video_dir, paste0(slug, "_occurrence_compare.mp4"))
  b64 <- base64encode(mp4_path)
  sprintf('
      <div class="clip">
        <h2>%s</h2>
        <video controls loop muted playsinline>
          <source src="data:video/mp4;base64,%s" type="video/mp4">
        </video>
      </div>', label, b64)
}

group_section <- function(group_label, clips) {
  clip_html <- paste(mapply(video_tag, clips, names(clips)), collapse = "")
  sprintf('
    <section>
      <h1 class="group-title">%s</h1>
      <div class="pair">%s
      </div>
    </section>
    ', group_label, clip_html)
}
```

Build each group's HTML, assemble the full page, and write it out.

```{r build-and-write}
video_blocks <- paste(mapply(group_section, names(pairs), pairs, SIMPLIFY = FALSE), collapse = "")

html <- sprintf('<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<title>LEAP_VOE Gaze Heatmaps</title>
<style>
  body { font-family: Avenir, "Avenir Next", -apple-system, BlinkMacSystemFont, sans-serif; background: #111; color: #eee; margin: 0; padding: 24px 24px 48px; }
  h1.page-title { font-weight: 500; margin: 0 0 8px; }
  .meta { color: #999; font-size: 0.9em; margin: 0 0 24px; }
  .meta p { margin: 0 0 2px; }
  .intro { max-width: 760px; color: #ccc; line-height: 1.5; margin: 0 0 36px; }
  .intro p { margin: 0 0 10px; }
  section { margin-bottom: 40px; }
  h1.group-title { font-weight: 500; font-size: 1.4em; margin: 0 0 12px; }
  h2 { font-weight: 500; font-size: 1.05em; margin: 0 0 6px; color: #4a90e2; }
  .pair { display: flex; flex-wrap: wrap; gap: 20px; }
  .clip { flex: 1 1 460px; min-width: 320px; }
  video { width: 100%%; display: block; border-radius: 6px; }
</style>
</head>
<body>
<h1 class="page-title">LEAP_VOE Gaze Heatmaps</h1>
<div class="meta">
<p>Authors: AJ Haskins and Tori Hennessy</p>
<p>Dates Videos Generated: %s</p>
<p>Total Number of Infants Included: %s</p>
</div>
<div class="intro">
<p>Each video is a stacked comparison of infants\' 1st test trial (top panel) vs. their 2nd test trial (bottom panel). In the LEAP_VOE experiment, infants see 2 familiarization trials followed by 4 test trials. </p>
<p>The heatmap overlay is a group-level (all subjects pooled) fixation density, computed over a sliding 2s time window that steps forward every 0.5s, composited over the video frame at each window\'s midpoint -- not a raw per-frame gaze trace. Windows run through movie playback and continue into the coding window, which lasts until each infant looks away (2s threshold) or 30s have passed. 

</p> The "n = " label in the top-right of each panel is the number of subjects with a fixation in that specific window; it shrinks over the course of the clip as infants look away.</p>
</div>
%s
</body>
</html>
', generated_date, n_infants_included, video_blocks)

writeLines(html, out_path)
message("Wrote ", out_path, " (", round(file.size(out_path) / 1e6, 1), " MB)")
```
