---
title: "Group Fixation-Density Heatmaps by Presentation Order"
output: html_document
---

## What this produces

For each of the 4 test trial types (expected_duck, surprise_duck,
expected_shoe, surprise_shoe), this renders one GIF with two stacked
panels: occurrence 1 (the infant's FIRST time seeing that clip, top panel)
above occurrence 2 (their SECOND time seeing it, bottom panel). Each
trial type is shown to a given infant twice (see the timing files -- e.g.
trials 5/6 and 9/10 are both "expected_duck", trials 7/8 and 11/12 are
both "surprise_shoe" for a subject who got that object/condition
assignment). This lets you visually compare whether gaze behavior differs
between the first and second exposure to the same event.

Each GIF steps through a SLIDING TIME WINDOW (default: 2s wide, sliding by
0.5s each step -- e.g. 0-2s, 0.5-2.5s, 1-3s, ...). Every step is a static
group-level (all subjects pooled) fixation-density heatmap for that
window, composited over the video frame at the window's midpoint. This is
NOT a smooth video with a moving heatmap overlaid frame-by-frame -- it's a
slideshow of overlapping snapshots, each one a "what did the group look at
during this ~2 second stretch" summary. That's a deliberate choice: with
infant fixation counts this low, a true per-video-frame (1/30s) heatmap
would have too few pooled points per frame to mean anything.

The windows run from movie start all the way through the end of the
STILL (frozen last-frame) period, not just through the movie itself.
STILL duration is NOT fixed -- it lasts until the infant looks away (or
caps at 30s by design), so different subjects contribute data for
different lengths of time. Because of that, every panel is annotated with
"n = X" (top-right, white text on a dark box) showing how many distinct
subjects actually have a fixation in THAT SPECIFIC window -- this number
will shrink over the course of the GIF as infants look away one by one.
Treat windows with a low n with appropriate skepticism; the heatmap shape
for e.g. n=2 is not a reliable group estimate.

## How to adapt this for other uses

- Change `WINDOW_SEC` / `STEP_SEC` below to make windows wider/narrower or
  more/less overlapping.
- Change the `video_map` list to point at different stimulus videos.
- The whole thing runs off `x_label_fixations.py`'s output, not raw gaze --
  if you want a raw-gaze version (denser, but no duration-weighting
  needed since raw samples arrive at a fixed rate), start from
  `voe_heatmap.Rmd`'s approach instead, which does that already.

## Why fixations instead of raw gaze

Unlike `voe_heatmap.Rmd`, which uses raw gaze samples, this was a
deliberate choice to use the I2MC fixation output from
`x_label_fixations.py` rather than raw continuous samples, so the heatmap
reflects "where the group actually looked" (post-filtering of
blinks/saccades/data loss) rather than every raw sample including noise.

## Duration weighting

A fixation that lasted 1000ms should count for more than one that lasted
40ms. `ggdensity::geom_hdr` has NO native `weight` aesthetic -- confirmed
by reading ggdensity's actual source (`StatHdr$compute_group` and
`get_hdr()` both only ever touch `data$x`/`data$y`, never a weight
column). So duration-weighting is faked by REPEATING each fixation's
(x, y) position once per `TICK_MS` of overlap between that fixation and
the current window (clipped to just the overlapping portion -- a fixation
that's only half inside a window contributes only that half's worth of
duration, not its full duration). More repeats = more influence on the
density estimate for that window. See `TICK_MS` below to change the
granularity of this.

## Bounds filtering

A fixation's gaze position can legitimately fall outside the physical
screen (0-1920 x 0-1080 px) -- I2MC doesn't clip to the display. Those
fixations are dropped BEFORE any windowing or plotting happens (see the
`filter(x >= 0, x <= SCREEN_WIDTH, ...)` call below), so they can never
contribute to (or bias) the density estimate, not merely be excluded from
the visual render. Note this filters to the full SCREEN bounds, not the
narrower stimulus/AOI bounds (1770x996) -- an infant can validly look at
blank screen space around the toy.

## Panel clipping

A subtler bug worth knowing about if you touch this code: ggdensity's KDE
grid defaults to the FULL plot scale range unless told otherwise via
xlim/ylim -- since this plot has two panels stacked into one canvas, that
means a density contour computed from the TOP panel's data could visually
bleed across the divider into the BOTTOM panel's space (and vice versa),
even though the underlying data points themselves never cross that line.
Confirmed by pixel-scanning the gap between panels before/after the fix.
Each `geom_hdr()` call below passes explicit xlim/ylim to constrain its
density grid to its own panel's half of the canvas -- don't remove those
or the bleeding comes back.

## Data source

The labeled fixation files from `x_label_fixations.py`
(`data/leap_voe_data/fixations/[subject]/[subject]_leap_voe_gaze_fix_labeled.csv`),
filtered to `phase %in% c("movie", "still")` -- i.e. excludes
attention-getter and inter-trial-interval fixations.

## Output

`data/leap_voe_data/gaze_heatmap_videos/gaze_occurrence/[trial_type]_occurrence_compare.gif`
(and a same-named .mp4, which is the higher-quality byproduct of building
the gif). This folder is gitignored, same as `voe_heatmap.Rmd`'s output --
these are meant to be regenerated locally from source data, not committed.
A full run (all 4 trial types) takes a few minutes.

```{r setup}
library(tidyverse)
library(png)
library(ggdensity)
library(here)
library(janitor)
```

## Config

`FRAME_RATE` must match the stimulus mp4s' actual encoded frame rate
(used both to extract frames via ffmpeg and to pick a window's background
frame). Sliding windows are `WINDOW_SEC` wide, advancing `STEP_SEC` at a
time. Duration-weighting repeats each fixation's (x, y) once per
`TICK_MS` of its overlap with a window. `WINDOW_GIF_FPS` is fixed at
`1 / STEP_SEC` so playback duration matches the real elapsed time of the
underlying window sequence (windows overlap since `STEP_SEC < WINDOW_SEC`,
so a fixed fps of 1 would make playback run `WINDOW_SEC / STEP_SEC` times
too long).

Screen/stimulus geometry mirrors how the "with_borders" stimulus videos
were built and displayed by PyHab (see `voe_heatmap.Rmd`'s config chunk
for the same numbers): full display is `SCREEN_WIDTH x SCREEN_HEIGHT`,
the stimulus is scaled to `STIM_WIDTH x STIM_HEIGHT` and centered, leaving
a border (`X_OFFSET`/`Y_OFFSET`) baked into the video pixels themselves
(its exact extent varies a bit by scene, so don't assume the area right
at the AOI edge is reliably dark -- this is why the "n =" label further
down uses an opaque box rather than bare white text).

```{r config}
FRAME_RATE   <- 30   # stimulus mp4s' actual encoded fps
MS_PER_FRAME <- 1000 / FRAME_RATE

WINDOW_SEC <- 2     # sliding window width, seconds
STEP_SEC   <- 0.5   # window step size, seconds (overlap = WINDOW_SEC - STEP_SEC)
TICK_MS    <- 20    # duration-weighting granularity: ms of overlap per repeated point

SCREEN_WIDTH  <- 1920
SCREEN_HEIGHT <- 1080
STIM_WIDTH    <- 1770
STIM_HEIGHT   <- 996
X_OFFSET      <- (SCREEN_WIDTH - STIM_WIDTH) / 2
Y_OFFSET      <- (SCREEN_HEIGHT - STIM_HEIGHT) / 2

WINDOW_GIF_FPS <- 1 / STEP_SEC   # windows/sec; keeps playback duration == real elapsed time
GIF_WIDTH      <- 700            # output gif width, px (height auto-scales)
```

Paths resolve via `here()` relative to the project root (`pill.Rproj`), so
this runs correctly regardless of working directory. GIFs/mp4s now save
into a `gaze_occurrence` subfolder of the existing heatmap output
directory.

```{r paths}
stimuli_path   <- here("stimuli", "leap_voe_stimuli", "videos", "with_borders")
fixations_dir  <- here("data", "leap_voe_data", "fixations")
timing_dir     <- here("data", "leap_voe_data", "raw_events", "timing")
output_folder  <- here("data", "leap_voe_data", "gaze_heatmap_videos", "gaze_occurrence")
frames_root    <- here("data", "leap_voe_data", "tmp_frames")  # scratch space, cleared per trial type

dir.create(output_folder, showWarnings = FALSE, recursive = TRUE)
dir.create(frames_root,   showWarnings = FALSE, recursive = TRUE)
```

Only the 4 test trial types get a GIF -- familiarization trials
(`fam_duck`/`fam_shoe`) are present in the fixation data but not rendered,
since each infant sees familiarization only once (no 1st-vs-2nd
comparison to make).

```{r video-map}
video_map <- c(
  "expected_duck"  = "duck_expected_bright.mp4",
  "surprise_duck"  = "duck_surprise_bright.mp4",
  "expected_shoe"  = "shoe_expected_bright.mp4",
  "surprise_shoe"  = "shoe_surprise_bright.mp4"
)
```

## Building the fixation table

For each subject, join their labeled fixations to their own timing file
to get every MOV trial's `startMoviePlayback` time, then duplicate it
under `trialNum + 1` so the paired STILL trial (always the next trialNum)
inherits the same t=0 anchor -- this puts movie and still fixations from
the same presentation on one continuous 0-based timeline. Subjects
missing a timing file (101, 107 as of writing) are skipped, matching
`x_label_fixations.py`'s own skip behavior.

```{r get-movie-starts}
get_movie_starts <- function(sub_id) {
  timing_path <- file.path(timing_dir, paste0(sub_id, "_leap_voe_timing.csv"))
  if (!file.exists(timing_path)) return(NULL)
  timing_raw <- read_csv(timing_path, show_col_types = FALSE)
  mov_starts <- timing_raw |>
    filter(event == "startMoviePlayback") |>
    select(trialNum, movie_start = time) |>
    mutate(movie_start = movie_start * 1000)  # timing files are in seconds; we work in ms
  still_starts <- mov_starts |> mutate(trialNum = trialNum + 1)  # STILL inherits its MOV trial's anchor
  bind_rows(mov_starts, still_starts)
}
```

For every subject's fixation file: keep only movie/still fixations with a
known trial type, join in movie start times, convert each fixation's
start/end to ms-since-that-trial's-movie-start, and drop any fixation
whose gaze position falls outside the physical screen (see "Bounds
filtering" above) before it can influence any density estimate.

```{r build-fixations}
fix_files <- list.files(fixations_dir, pattern = "_fix_labeled\\.csv$",
                         recursive = TRUE, full.names = TRUE)
message("Found ", length(fix_files), " labeled fixation files")

all_fixations <- map_dfr(fix_files, function(f) {
  sub_id <- str_remove(basename(f), "_leap_voe_gaze_fix_labeled\\.csv$")

  movie_starts <- get_movie_starts(sub_id)
  if (is.null(movie_starts)) return(tibble())  # no timing file -- skip subject

  fix_df <- read_csv(f, show_col_types = FALSE) |> clean_names()  # startT -> start_t, etc.

  movie_fix <- fix_df |>
    filter(phase %in% c("movie", "still"), !is.na(trial_num), trial_type != "") |>
    inner_join(movie_starts, by = c("trial_num" = "trialNum"))

  if (nrow(movie_fix) == 0) return(tibble())

  movie_fix |>
    transmute(
      sub_id = sub_id,
      trial_type = trial_type,          # e.g. "expected_duck_1" (includes occurrence suffix)
      start_rel = start_t - movie_start, # ms since this trial's own movie start
      end_rel   = end_t - movie_start,
      x = xpos,   # I2MC fixation x, screen pixel space (top-left origin)
      y = ypos    # same, y-down
    ) |>
    filter(x >= 0, x <= SCREEN_WIDTH, y >= 0, y <= SCREEN_HEIGHT)  # drop off-screen fixations
})

message("Total movie+still fixations (in-bounds): ", nrow(all_fixations))
message("Trial types present: ", paste(sort(unique(all_fixations$trial_type)), collapse = ", "))
```

## Sliding windows and duration weighting

`build_windows()` generates the sequence of sliding windows covering
`[0, total_ms]` (`WINDOW_SEC` wide, starting every `STEP_SEC`; the last
window is truncated to end exactly at `total_ms`). Each window's
`mid_frame` is the background video frame to composite it over -- the
frame at the window's temporal midpoint, later clamped to the last real
frame during the STILL period so the display correctly "freezes".

`expand_to_windows()` implements the duration-weighting scheme described
above: each fixation's (x, y) is repeated once per `TICK_MS` of its
overlap with a given window, clipped to just the overlapping portion. A
fixation with zero overlap with a window contributes nothing to it.

```{r windowing-functions}
build_windows <- function(total_ms) {
  window_ms <- WINDOW_SEC * 1000
  step_ms   <- STEP_SEC * 1000
  w_start <- seq(0, total_ms - window_ms, by = step_ms)
  if (length(w_start) == 0) w_start <- 0  # clip shorter than one window -- use a single window
  tibble(
    window_idx = seq_along(w_start),
    w_start = w_start,
    w_end   = pmin(w_start + window_ms, total_ms),
    mid_frame = pmax(1, floor(((w_start + pmin(w_start + window_ms, total_ms)) / 2) / MS_PER_FRAME) + 1)
  )
}

expand_to_windows <- function(fixations_df, windows) {
  if (nrow(fixations_df) == 0) return(tibble())

  map_dfr(seq_len(nrow(windows)), function(i) {
    w_start <- windows$w_start[i]
    w_end   <- windows$w_end[i]

    overlap_start <- pmax(fixations_df$start_rel, w_start)
    overlap_end   <- pmin(fixations_df$end_rel, w_end)
    overlap_ms    <- overlap_end - overlap_start

    keep <- overlap_ms > 0
    if (!any(keep)) return(tibble())

    n_reps <- pmax(1, round(overlap_ms[keep] / TICK_MS))  # >=1 rep even for a brief overlap

    tibble(
      sub_id = fixations_df$sub_id[keep],
      window_idx = windows$window_idx[i],
      x = fixations_df$x[keep],
      y = fixations_df$y[keep]
    ) |>
      uncount(n_reps)
  })
}
```

## Rendering one trial type's comparison GIF

`render_occurrence_comparison()` builds one stacked GIF (occurrence 1 on
top, occurrence 2 on bottom) for a given base trial type:

- Extracts every frame of the stimulus video via ffmpeg (the actual
  bordered video shown to infants), and splits `all_fixations` into this
  trial type's 1st vs. 2nd presentation (`_1`/`_2` suffix). Subject sets
  for occurrence 1 and 2 aren't guaranteed identical -- a subject can have
  usable data for one presentation but not the other.
- Sliding windows run for however long is greater: the movie's own
  length, or the latest fixation end-time across either occurrence
  (STILL can extend well past the movie, capped at 30s by design, and
  differs by subject) -- this keeps both panels sharing one window
  sequence, so `window_idx` means "same relative time since movie start"
  in both panels.
- Each window's plot composites the background video frame with a
  `geom_hdr()` density layer per occurrence, using I2MC (x, y) positions
  flipped from y-down/pixel-space to ggplot's y-up (no rescaling needed --
  I2MC positions are already in pixel space, unlike `voe_heatmap.Rmd`'s
  normalized 0-1 gaze coords). `xlim`/`ylim` are passed explicitly to each
  `geom_hdr()` call to keep its KDE grid inside its own panel (see "Panel
  clipping" above).
- `has_spread()` + `tryCatch` guard against `MASS::kde2d()`'s "bandwidths
  must be strictly positive" error, which happens when a window's points
  have near-zero (x, y) variance (e.g. one subject's one fixation,
  duration-repeated) -- that window just renders without a heatmap layer
  for that occurrence instead of crashing the run.
- The "n = " subject-count box is added last (after the density layers)
  so it always draws on top, and uses an opaque background rather than
  bare white text since the bordered stimulus videos have their own
  baked-in white letterboxing plus variable scene brightness in that
  corner.
- Frames are compiled to mp4, then to GIF via ffmpeg's two-pass palette
  generation (`palettegen`/`paletteuse`, better color quality than a
  naive single-pass conversion), and per-trial-type scratch frames are
  deleted at the end.

```{r render-function}
render_occurrence_comparison <- function(base_trial_type) {
  message("\n=== ", base_trial_type, " ===")

  video_file <- file.path(stimuli_path, video_map[[base_trial_type]])
  frame_split_path <- file.path(frames_root, paste0("split_", base_trial_type))
  frame_merge_path <- file.path(frames_root, paste0("merge_", base_trial_type))
  dir.create(frame_split_path, showWarnings = FALSE)
  dir.create(frame_merge_path, showWarnings = FALSE)

  message("Extracting frames from: ", basename(video_file))
  system(paste0(
    'ffmpeg -y -i "', video_file, '" -vf "fps=', FRAME_RATE, '" "',
    frame_split_path, '/frame_%04d.png"'
  ))
  n_frames <- length(list.files(frame_split_path, pattern = "^frame_[0-9]{4}\\.png$"))
  movie_ms <- n_frames * MS_PER_FRAME
  message("Extracted ", n_frames, " frames (", round(movie_ms/1000, 1), "s movie)")

  occ1_fix <- all_fixations |> filter(trial_type == paste0(base_trial_type, "_1"))
  occ2_fix <- all_fixations |> filter(trial_type == paste0(base_trial_type, "_2"))
  message("Occurrence 1: ", n_distinct(occ1_fix$sub_id), " subjects, ", nrow(occ1_fix), " fixations")
  message("Occurrence 2: ", n_distinct(occ2_fix$sub_id), " subjects, ", nrow(occ2_fix), " fixations")

  max_fix_ms <- suppressWarnings(max(c(occ1_fix$end_rel, occ2_fix$end_rel), na.rm = TRUE))
  total_ms <- max(movie_ms, max_fix_ms, na.rm = TRUE)
  if (!is.finite(total_ms)) total_ms <- movie_ms  # no fixations at all for this trial type

  windows <- build_windows(total_ms)
  message("Built ", nrow(windows), " sliding windows (", WINDOW_SEC, "s window, ", STEP_SEC, "s step, ",
          round(total_ms/1000, 1), "s total incl. STILL)")

  occ1 <- expand_to_windows(occ1_fix, windows)
  occ2 <- expand_to_windows(occ2_fix, windows)

  canvas_w <- SCREEN_WIDTH
  canvas_h <- SCREEN_HEIGHT * 2   # one screen wide, two screens tall (occ1 top half, occ2 bottom half)

  walk(seq_len(nrow(windows)), function(i) {
    w <- windows[i, ]
    message("  window ", i, " of ", nrow(windows), ": ",
            round(w$w_start/1000, 1), "-", round(w$w_end/1000, 1), "s (frame ", w$mid_frame, ")")

    img_path <- file.path(frame_split_path, sprintf("frame_%04d.png", min(w$mid_frame, n_frames)))  # clamp into STILL freeze
    out_path <- file.path(frame_merge_path, sprintf("window_%04d.png", i))
    frame_img <- as.raster(readPNG(img_path))

    g1 <- occ1 |> filter(window_idx == w$window_idx) |>
      mutate(px = x, py = (SCREEN_HEIGHT - y) + SCREEN_HEIGHT)  # y-flip + shift into top half
    g2 <- occ2 |> filter(window_idx == w$window_idx) |>
      mutate(px = x, py = SCREEN_HEIGHT - y)  # y-flip only, bottom half

    n_sub1 <- n_distinct(g1$sub_id)
    n_sub2 <- n_distinct(g2$sub_id)

    p <- ggplot() +
      theme_void() +
      theme(legend.position = "none",
            panel.background = element_rect(fill = "white", color = NA),
            plot.margin = margin(0, 0, 0, 0)) +
      annotation_raster(frame_img, xmin = X_OFFSET, xmax = X_OFFSET + STIM_WIDTH,
                         ymin = Y_OFFSET + SCREEN_HEIGHT, ymax = Y_OFFSET + STIM_HEIGHT + SCREEN_HEIGHT) +
      annotation_raster(frame_img, xmin = X_OFFSET, xmax = X_OFFSET + STIM_WIDTH,
                         ymin = Y_OFFSET, ymax = Y_OFFSET + STIM_HEIGHT) +
      geom_hline(yintercept = SCREEN_HEIGHT, color = "grey40", linewidth = 0.5) +
      annotate("text", x = 20, y = canvas_h - 20,
               label = paste0("1st exposure  |  ", round(w$w_start/1000, 1), "-", round(w$w_end/1000, 1), "s"),
               hjust = 0, vjust = 1, size = 5, color = "black") +
      annotate("text", x = 20, y = SCREEN_HEIGHT - 20,
               label = paste0("2nd exposure  |  ", round(w$w_start/1000, 1), "-", round(w$w_end/1000, 1), "s"),
               hjust = 0, vjust = 1, size = 5, color = "black")

    has_spread <- function(df) nrow(df) >= 3 && sd(df$px) > 0 && sd(df$py) > 0  # kde2d needs spread in both dims

    if (has_spread(g1)) {
      p <- tryCatch(
        p + geom_hdr(data = g1, aes(px, py, fill = after_stat(probs)), alpha = 0.5,
                      xlim = c(0, SCREEN_WIDTH), ylim = c(SCREEN_HEIGHT, canvas_h)),
        error = function(e) { message("  window ", i, " occ1 density failed: ", e$message); p }
      )
    }
    if (has_spread(g2)) {
      p <- tryCatch(
        p + geom_hdr(data = g2, aes(px, py, fill = after_stat(probs)), alpha = 0.5,
                      xlim = c(0, SCREEN_WIDTH), ylim = c(0, SCREEN_HEIGHT)),
        error = function(e) { message("  window ", i, " occ2 density failed: ", e$message); p }
      )
    }

    p <- p +   # n= boxes added last so they always draw on top of the heatmap
      annotate("rect", xmin = canvas_w - 170, xmax = canvas_w - 10,
               ymin = canvas_h - 55, ymax = canvas_h - 10,
               fill = "black", alpha = 0.55) +
      annotate("text", x = canvas_w - 20, y = canvas_h - 20,
               label = paste0("n = ", n_sub1),
               hjust = 1, vjust = 1, size = 5, color = "white") +
      annotate("rect", xmin = canvas_w - 170, xmax = canvas_w - 10,
               ymin = SCREEN_HEIGHT - 55, ymax = SCREEN_HEIGHT - 10,
               fill = "black", alpha = 0.55) +
      annotate("text", x = canvas_w - 20, y = SCREEN_HEIGHT - 20,
               label = paste0("n = ", n_sub2),
               hjust = 1, vjust = 1, size = 5, color = "white")

    p <- p +
      scale_x_continuous(limits = c(0, canvas_w), expand = c(0, 0)) +
      scale_y_continuous(limits = c(0, canvas_h), expand = c(0, 0)) +
      coord_fixed()  # 1:1 aspect so the composited video isn't stretched

    tryCatch(
      ggsave(out_path, plot = p, width = canvas_w / 100, height = canvas_h / 100,
             units = "in", dpi = 100),
      error = function(e) message("  window ", i, " failed: ", e$message)
    )
  })

  message("Compiling windows -> mp4 -> gif")
  mp4_path <- file.path(output_folder, paste0(base_trial_type, "_occurrence_compare.mp4"))
  gif_path <- file.path(output_folder, paste0(base_trial_type, "_occurrence_compare.gif"))
  palette_path <- file.path(tempdir(), paste0(base_trial_type, "_palette.png"))

  system(paste0(
    'ffmpeg -y -framerate ', WINDOW_GIF_FPS, ' -i "', frame_merge_path, '/window_%04d.png" ',
    '-c:v libx264 -vf format=yuv420p "', mp4_path, '"'
  ))
  system(paste0(   # optimized 256-color palette, better quality than ffmpeg's default gif encoder
    'ffmpeg -y -i "', mp4_path, '" -vf "fps=', WINDOW_GIF_FPS, ',scale=', GIF_WIDTH, ':-1:flags=lanczos,palettegen" "',
    palette_path, '"'
  ))
  system(paste0(
    'ffmpeg -y -i "', mp4_path, '" -i "', palette_path, '" ',
    '-filter_complex "fps=', WINDOW_GIF_FPS, ',scale=', GIF_WIDTH, ':-1:flags=lanczos[x];[x][1:v]paletteuse" "',
    gif_path, '"'
  ))

  unlink(frame_split_path, recursive = TRUE)  # per-trial-type scratch, nothing left but final mp4/gif
  unlink(frame_merge_path, recursive = TRUE)
  message("Saved: ", gif_path)
}
```

## Run

Renders all 4 trial types' comparison GIFs (a full run takes a few
minutes).

```{r run-all}
for (tt in names(video_map)) {
  render_occurrence_comparison(tt)
}

message("\nAll done. GIFs in: ", output_folder)
```

Writes a small metadata sidecar (`generation_info.csv`, in `output_folder`)
recording when this run happened and how many distinct infants
contributed a fixation to any of the 4 rendered trial types -- consumed
by `x_gaze_occurrence_gallery.Rmd` for its "generated on" / "infants
included" header text.

```{r write-metadata}
n_infants_included <- all_fixations |>
  filter(str_remove(trial_type, "_[12]$") %in% names(video_map)) |>
  distinct(sub_id) |>
  nrow()

tibble(generated_at = Sys.time(), n_infants_included = n_infants_included) |>
  write_csv(file.path(output_folder, "generation_info.csv"))

message("Infants included across all 4 test trial types: ", n_infants_included)
```
